---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tsforest

<!-- badges: start -->
<!-- badges: end -->

The goal of tsforest is to provide an R implementation of the Time Series Forest classification algorithm described by Deng et al (2013) and documented on timeseriesclassification.com. There's another R package that implements many of these, but its backend is in Java which can cause some installation and running problems.

## Installation

You can install the the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mattsq/tsforest")
```

This is still very much a work in progress! Eventually I'd like to S3-ize the model objects, build tests and more example data, and in general make it a more properly-featured model package.

## Usage

The package is pretty easy to use! Here's a simple example:

```{r fit_model_1}
library(tsforest)
data("FreezerRegularTrain_TRAIN")
data("FreezerRegularTrain_TEST")
model <- tsforest(FreezerRegularTrain_TRAIN, target = "target")
print(model)
```

Predictions use the standard S3 predict method, and return a vector of predictions:

```{r predict_model_1}
preds <- predict(model, FreezerRegularTrain_TEST)
table(preds$predictions, FreezerRegularTrain_TEST$target)
```

There's also a more experimental (and not at all theoretically grounded!) function that takes advantage of the fact that variables are (partially) defined as intervals to plot the variable importance across the time series interval. You can use any summary function, although sum seems to work the best:

```{r intervalwise_model_1}
model <- tsforest(FreezerRegularTrain_TRAIN, 
                  importance = 'permutation', 
                  verbose = FALSE)
intervalwise_variable_importance(model, summary_function = sum)
```

You can also plot an individual example using the function, where the example will be scaled correctly to the importance values:

```{r intervalwise_with_example}
intervalwise_variable_importance(model, 
                                 summary_function = sum, 
                                 optional_example_rownumber = 1)
```

