---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tsforest

<!-- badges: start -->
<!-- badges: end -->

The goal of tsforest is to provide an R implementation of the Time Series Forest classification algorithm described by Deng et al (2013) and documented on timeseriesclassification.com. There's another R package that implements many of these, but its backend is in Java which can cause some installation and running problems.

## Installation

You can install the the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mattsq/tsforest")
```

This is still very much a work in progress! Eventually I'd like to S3-ize the model objects, build tests and example data, and in general make it a more properly-featured model package.

## Usage

The package is pretty easy to use! Here's a simple example:

```{r}
library(tsforest)
data("LargeKitchenAppliances_TRAIN")
data("LargeKitchenAppliances_TEST")
model <- tsforest(LargeKitchenAppliances_TRAIN)
preds <- predict_tsforest(model, LargeKitchenAppliances_TEST)
table(preds$predictions, LargeKitchenAppliances_TEST$target)
```


